---
title: "Code to Randomly Select Grid Squares on Blood Slides"
author: "Cory McKinstry"
format: pdf
---

**Context:** We have hundreds of blood slides that we want to do cell counts on. We recently purchased a stamp that we can use to find random positions on the blood slides that we can take photographs of, then complete cell counts on.

**Goal:** Based on an 8x8 grid where columns are A-H and rows are 1-8, randomly select grid cell values to use as picture locations on the blood slides.

## Loading Packages

```{r}
#| message: false

library(tidyverse)
```

## Creating Dataframe of Values

```{r}
columns <- c("A", "B", "C", "D", "E", "F", "G", "H")
#If you're doing two stamps per slide, extend columns to P
rows <- seq(1, 8, 1)

combinations <- expand.grid(
  columns = columns, rows = rows)

combinations$combinations <- paste(
  combinations$columns, combinations$rows, sep="")
```

## Creating Random List from Values

```{r}
set.seed(123) #For reproducibility, change for new random values

random.list <- sample(
  combinations$combinations,
  1000, #Length of the random list
  replace = TRUE,
  prob = NULL)
```

## Full list

```{r}
random.list
```

